\chapter{Discussion}\label{chapter:discussion}
While developing the application for this project, multiple problems were found, resulting in inaccurate dead reckoning positioning.
Although many of the problems were solved, some problems still exist, which causes the dead reckoning to be inaccurate.
Possible solutions to the existing problems in the application will be examined and discussed in further development, \secref{section:further-development}.

Apart from the existing problems, implementation decisions, made during development of this application, are discussed in this chapter.
Furthermore, the application will be compared to existing systems to determine the pros and cons of this application.

\subsection*{Platform}
The application that is developed for this project is currently working on Windows Phone 8 platform.
The choice of developing for Windows Phone 8 gives the opportunity to distribute to a large market, where Windows Phone 8 had $4.2$ million users in 2012 \citep{misc:wp8-users}.
The market could, however, be expanded if the application was to be developed for other platforms as well, but the Windows Phone 8 platform still allows for a large market.
However, with the amount of time at hand the resources were allocated to develop a dead reckoning application for a single platform, as the focus was to make dead reckoning work, rather than distributing the application for multiple platforms. 

Furthermore, the variance for the acceleration is determined for one accelerometer and thus the variance is not directly portable to other phones, which may have other variances for the acceleration even if they have the same accelerometer model.
For that reason, it could be argued that when the application is first used, the phone should be placed on a flat surface for a given time period to determine the variance of the acceleration for that specific accelerometer.

\subsection*{One Dimension}
For the scope of this project, dead reckoning has been implemented for one dimension.
It was done to simplify how movements could look, thus making dead reckoning easier to implement.
%It is undesirable to track movement in only one dimension, since it limits the part of the movement traced.

A constraint was that the user should do sideways movements.
However, this constraint was not a problem since the application only needed one dimensional movements and there are a lot of arcade games that just need one dimensional movements.

The movement tracking could be in two dimensions for a planar surface, or even in three dimensions when there is a desire to track vertical movement as well.
Movement tracking in two dimensions, could be possible by keeping track of the phone's heading.

Three dimensions would make tracking more complex, since it would require something to track the movement in three axis.
However, with more time, tracking jumps could potentially be pursued as it would not require additional environmental constraints, other than a place where it is possible to jump freely.

\subsection*{Pedestrian Dead Reckoning}
The application developed for this project was an algorithm using pedestrian dead reckoning to track the user's movements. 
It gave certain opportunities, while removing others.
The fact that pedestrian dead reckoning uses the sensors of the phone itself, with no dependencies from other sources, could be used to track the user's movement.

Pedestrian dead reckoning gave the advantage that extra equipment, such as a Wi-Fi beacon, was not needed, and was the primary reasoning for using pedestrian dead reckoning.
However, it also limited the scope of what information could be used to determine the movement of the user.
A problem when not using such information, was that after some time, the pedestrian dead reckoning became highly inaccurate and the variance would be higher. 
This would result in a higher uncertainty.
However, implementing position tracking by another method could be used as evidence on the Bayesian network. 
This other method could be implemented in conjunction with the pedestrian dead reckoning as an extended Kalman filter to increase the accuracy of dead reckoning. 

\subsection*{Motivation}
Various features were implemented in the game developed, to motivate people to play the game. 
These features included a high score, power-ups, and increasing difficulty.

The high score simply shows the highest scores achieved on the device.
%For the highscore it is possible to see the highest score of the user, and thereby see the progression.
Furthermore, the high score is intended to make the user compete against other users, thereby making people want to play more to improved their score or to be better than their friends.

To make the game entertaining, power ups and increasing ball speed were implemented, since it was believed that without those features the game would become tedious and thus less entertaining. 

As mentioned above, features have been implemented to make the game entertaining and at the same time make people exercise.
Whether the features make the game entertaining and motivates the users towards exercise, has not been examined.
In order to examine this, the target audience of the application would have to be involved to test the game and give feedback on what they find entertaining.
Furthermore, a fitness consultant could be contacted to determine whether the movement patterns needed to play the game is good exercise or not.

\input{content/discussion/perspective}

\input{content/discussion/further-development}