\section{Motivation}\label{section:motivation}
Motivation is good when starting to exercise, because after the first couple of weeks people tend to lose motivation and stop exercising. 
There are many factors to keep a user motivated.
These factors affect people differently and it is therefore near impossible to get everybody motivated. 
However, instead of motivating people to do exercise, a fun game can be made, that people like to play and indirectly, by playing the game, physical activity is achieved.
Good motivation leads to frequent exercises, since it is fun doing them \citep{misc:gamemotivations}.

Motivation can be amplified by making the game able to track the user's exercise and compare it with others.
It does not necessarily have to be how hard the user has exercised, but instead how well they performed in the game, as well as other ways to make the game entertaining and interesting.

To elaborate more on the approach for motivation that will be used in this project, various factors can be considered when making a game that is fun, immersive, and addictive.
The game is meant to motivate people to indirectly do exercise.
It will be a game with controls as in old arcade games such as \textit{Falldown, Break-it, Space Invaders,} and \textit{Pong}, where the user, in this case, is the controller.

Apart from the mentioned properties, other features could be a high score, so the user is able to see if he is better than his friends, which can keep the competitive users motivated.
A high score can, arguably, be de-motivational if the user is compared to people with a higher score.
On the other hand, it can also be motivating for people who are not giving up, since they want a better score than their friends.
Generally, people like to be rewarded for their progress, this reward could be upgrades.
When making upgrades, it is important that the upgrades are achievable in a reasonable amount of time.
Furthermore, since the game attempts to get the user to exercise, the upgrades should not lower the amount of exercise that the user gets.
Therefore, upgrades could be additional movement, such as, jumping, moving forward etc. to add additional exercise patterns.

% Andre motivation factors der skal skrives om selve gamet

% ranking/highscore

% progess

% action

% etc.