\section{Sensors}\label{section:sensors}
The game for this project is intended to make people exercise, and it is therefore necessary that the game can track the users' movement.
As a result, it is crucial that the platform, which the game is running on, has the sensors needed.
Fortunately, this is the case for many smartphones.
The necessary sensors to track the users' movement will be thoroughly examined.

\subsection{Accelerometer}
An accelerometer is a sensor that is used to track the acceleration of a given device and the information tracked is represented in three values.
The three values are the acceleration in the x-, y-, and z-axis.
The accelerometer can simulate a pedometer, where the differences in the acceleration values can be recognised as a step, this technique can be used in dead reckoning.
The difference between a pedometer and an accelerometer is that the pedometer can only count steps, where the accelerometer readings can be used to calculate how far the steps are.
Furthermore, the accelerometer is not limited to function as a pedometer and can use the tracked acceleration for other calculations such as game input.
For this project the accelerometer can be used to track the user's movements. 

\subsection{Gyroscope}
A gyroscope is a sensor that is used to track the orientation of a given device, this information is represented in three values.
These values are the orientation in the three axes.
The gyroscope can be used as a compass, to do this the device has to know precisely which way is north before it can calculate which way the device is orientated.
However, the measurement uncertainty can become a great concern the more the device is turned.
The gyroscope can be used when creating dead reckoning algorithms, since it can calculate which way the device is orientated to determine when the device is turned.

\subsection{Magnetometer}
A magnetometer is a sensor which is used to track the magnetic field of the earth, but can also be affected by other magnetic fields.
The magnetometer can show how the device is orientated, compared to the magnetic poles.
The information can be used to track if the user is turning around.
The magnetometer can help adjust the measurement uncertainty of the gyroscope.