\section{Perspective}
With the dead reckoning exercise application developed for this project, the application can be compared to other existing exercise systems that is described in \secref{section:existing-systems}.

The game that has been developed is for exercise purposes.
It is believed that Endomondo and Zombies, Run! have the potential to evoke exercise on a more intensive level, due to the nature of running versus sidestepping.
However, Moves does not in itself lead to exercise as the developed application, but tracks the progress of a whole day and not only when the user wants to exercise.

When using applications that induce or track exercise, the user should gain some value from it.
For this project the primary focus was entertaining exercise, while systems such as Endomondo and Moves gives the value of tracking the exercise performed.
A system that has been examined in this project and gives entertainment value is Zombies, Run!.
Zombies, Run! brings an interesting storyline, written by professional authors and performed by professional narrators, while running.
Furthermore, it entertains the user while exercising, however, if a user does not like the story, the primary entertainment value of the Zombies, Run! is counter productive, as the user would then stop playing due to him perceiving that it is a bad story.
The developed application is for the user to entertain himself by playing the game and achieving a better high score. 
However, therein lies the problem that there is no storyline to make the user motivated to play the game, and thus the game may become a tedious experience.

When doing exercise, information about progress, such as, calories burned or the amount of exercise performed can be presented.
The application was developed to make the user have fun when doing exercise, and thereby motivate people, after having used the application, to begin doing other more intensive types of exercise afterwards.
Therefore, information about calories burned and the amount of exercise performed was not an important part, as it is for Endomondo, Moves, and Zombies, Run!.
Implementing tracking of the amount of exercise performed when using the application could be an additional feature that motivates people.
However, due to the primary focus being dead reckoning and embedded systems, exercise statistics have  not been a concern.

As discussed, the application developed differs in various ways from the existing systems described in \secref{section:existing-systems}, and has had a different approach to exercise.
The developed application is deemed to be different than the other systems.
It serves a different purpose where the user plays with his movement and exercise comes as a bonus, in contrast to the other systems, where exercise has a more central and visible role. 
In that regard, the developed application is not unique when it comes to the game itself, but it is the movement tracking by dead reckoning, working as the controller, which makes the developed application interesting.