\section{Requirements}\label{section:requirements}
In this project there is a set of requirements that should be met.
The purpose of the project is to develop a game which makes users exercise, tracking the movement with dead reckoning.
The hard and soft requirements for the application will be described and reasoned for hereafter.

\subsection{Hard Requirements}
The hard requirements are the essential requirements of the application.
\subsubsection*{Exercise}
The application to be developed is meant to be a game application with exercise in mind. 
Therefore, physical activity is required from the user.
Since the user has to walk left and right in order to play the game, this is considered cardiovascular exercise.
While there are many different forms of exercise, the focus of this application is to encourage physical activity to lose weight.
However, various forms of cardiovascular exercise would be a great addition to the application, but due to the time constraints of this project such exercise variations are not pursued. 

\subsubsection*{Dead Reckoning}
As previously mentioned in \secref{section:dead-reckoning}, dead reckoning is able to track a user's movement more precisely on a small scale, compared to the GPS and works indoor.
Understanding and implementing dead reckoning is a key goal of the project, as the intent of this semester is to acquire knowledge of machine intelligence.
Dead reckoning will be used in the game to control the movements inside the game.
These movements will, as mentioned, make the user physically active.
Another result of using dead reckoning, is that the game will be playable everywhere without relying on non-embedded hardware.

\subsubsection*{Game}
The final application should be a game that includes all the hard requirements, seen above. 
The game has to be controlled by the player, whom can move in one axis, meaning that a player can move both left and right.
The game type should be similar to Space Invaders, Pong, and Break-It.
One of the key points of making the application a game, is to motivate people. 
The requirement includes the game, itself, while additional motivational features, such as high scores, are not included in this requirement.

\subsection{Soft Requirements}
If the application has met the hard requirements and there is enough time, the soft requirements can be implemented.

\subsubsection*{Two Dimensional Movement} 
Two dimensional (2D) movement is an extension to the movement allowed and needs adjustments in the dead reckoning techniques.
If it proves to be easy to develop control for one axis, the scope of the project will be extended to 2D movement. 
Which means if 2D movement is implemented, controls will allow for other types of games, e.g. moving in a labyrinth as in Pacman, which will result in other movement patterns.

\subsubsection*{Motivational Features}
Motivational features can be implemented to make the user start and continue playing the game.
Some motivational features could be high scores, in which users can compare and compete amongst each other, resulting in increased replay value.  
Other features that can affect the replay value could be achievements in the game as well as different levels or difficulties.
Additional motivational features can be seen in \secref{section:motivation}.