\section{Events}\label{section:event-table}
The event table in \tabref{table:event-table} represents the possible events in the game and how they are connected to the classes.
The classes used are \textit{Paddle}, \textit{Ball}, \textit{Time}, and \textit{Score}.
The Paddle class ensures that the movements of the player corresponds to the paddle in the game.
The Ball class represents the ball which moves on the board, and can bounce off the walls and the paddle. 
Time starts when the game starts and stops when the ball is not caught.
Time is also used to limit the duration of power-ups and increases the score as time passes.

\begin{table}[h]
\centering
\begin{tabular}{| c | c | c | c | c |}
\hline
 & Paddle & Ball & Time & Score \\\hline
Lose game & & + & + & + \\ \hline
Move & * & & & \\ \hline 
Spawn ball & & + & &  \\\hline
Despawn ball & & + & &  \\\hline
Spawn power-up & & & * & \\\hline
Change paddle size  & * & & & \\\hline
Increase ball speed & & * & * & \\\hline
Decrease ball speed & & * & & \\\hline
Increase score & & & * & *\\\hline
Score multiplier & & & & * \\\hline
\end{tabular}
\caption{Event Table, * meaning zero to many and + meaning zero to one.}
\label{table:event-table}
\end{table}

\textit{Lose game} is an event that happens when the ball is not caught by the paddle. 
When the event occurs, the time is stopped and the Score is saved in case the user wants to submit it to the high score.
To avoid losing the game, the paddle has to be able to move.
The \textit{Move} event works together with dead reckoning to get the movement of the player, and enables the paddle to move left and right.

\textit{Spawn power-up} is an event that spawns a power-up in the game, which occurs randomly after some time.
One of the power-ups that can spawn is a power-up that increases the paddle size and the counterparting power-up decreases the paddle size.

The ball spawns when the game starts, and despawns when the ball is not caught.
This is handled by the \textit{Spawn ball} and \textit{Despawn ball} events.
The ball speed is increased over time, but can also be changed with the help of power-ups, which is the \textit{Increase ball speed} and \textit{Decrease ball speed} event.

The score can be affected by two different events.
\textit{Increase score} happens over time, whereas \textit{Score multiplier} occurs when its corresponding power-up is caught, resulting in either a doubling or halving of the score, depending on the power-ups colour.
